Towards Proof-Reconstruction of Problems in Classical Propositional Logic

### 2017-09-26 paper/sections/proof-reconstruction.tex
[ paper ] working on resolve rule.

\begin{theorem}[thm-reorder$_{∨}$] $Γ ⊢ φ$, and $ψ\in\Prop$ then $Γ ⊢ reorder_{∨}(φ, ψ)$, where,
\begin{equation*}
  \label{eq:reorder-or}
  reorder_{∨} (φ, ψ) = strongBuild_{∨}(rdisj(φ), ψ).
\end{equation*}
\end{theorem}
\begin{proof} Use Lemma~\ref{lem:lem-rdisj} and Lemma~\ref{lem:lem-sbuild-or}.
\end{proof}

@@

\begin{align}
    \begin{split}
    reorder_{∧∨}(φ, ψ)=
      \begin{cases}
        ψ &\text{if } φ≡ψ,\\
        ψ &\text{if } ψ ≡ ψ₁ ∧ ψ₂, reorder_{∧∨}(φ,ψ₁) ≡ ψ₁,\\
          &\text{and }reorder_{∧∨}(φ, ψ₂) ≡ ψ₂,\\
        φ &\text{if }ψ ≡ ψ₁ ∧ ψ₂,\\
        conjunct_{∨}(φ, ψ) &\text{otherwise.}
      \end{cases}
    \end{split}
\end{align}

\end{theorem}

>>>>

\begin{theorem}[thm-reorder$_{∨}$]
$Γ ⊢ φ$, and $ψ\in\Prop$ then $Γ ⊢ reorder_{∨}(φ, ψ)$, where,
\begin{equation*}
  \label{eq:reorder-or}
  reorder_{∨} (φ, ψ) = strongBuild_{∨}(rdisj(φ), ψ).
\end{equation*}
\end{theorem}

\begin{proof} Use Lemma~\ref{lem:lem-rdisj} and Lemma~\ref{lem:lem-sbuild-or}.
\end{proof}

@@

\begin{align}
    \begin{split}
    reorder_{∧∨}(φ, ψ)=
      \begin{cases}
        ψ &\text{if } φ≡ψ,\\
        ψ &\text{if } ψ ≡ ψ₁ ∧ ψ₂, reorder_{∧∨}(φ,ψ₁) ≡ ψ₁,\\
          &\text{and }reorder_{∧∨}(φ, ψ₂) ≡ ψ₂,\\
        φ &\text{if }ψ ≡ ψ₁ ∧ ψ₂,\\
        conjunct_{∨}(φ, ψ) &\text{otherwise.}
      \end{cases}
    \end{split}
\end{align}
\end{theorem}

\subsubsection{Resolve.} The \resolve rule is a generalization version for resolution in propositional logic since the formulas are not shaped always as the theorem expect (see Fig.~\ref{fig:metis-inferences}).

Since our approach is mere syntactic, in order to apply such a
theorem, we perform rearrangements inside the formulas to match with
the pattern expected by the resolution theorem.

\begin{lemma}[lem-resolution]
